Plots and tables summarizing results of Poisson simulations

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.b.1 = colMeans(matrix(c(mise.hf.ti.r.4.b.1, mise.hf.ti.r.5.b.1, mise.hf.ti.r.6.b.1, mise.hf.ti.r.7.b.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.8 = colMeans(matrix(c(mise.hf.ti.r.4.b.8, mise.hf.ti.r.5.b.8, mise.hf.ti.r.6.b.8, mise.hf.ti.r.7.b.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.128 = colMeans(matrix(c(mise.hf.ti.r.4.b.128, mise.hf.ti.r.5.b.128, mise.hf.ti.r.6.b.128, mise.hf.ti.r.7.b.128), byrow = TRUE, nr = 4))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

>>>>

```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```
